### 2023-10-27 manuscript.tex
update intro [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/6668399835

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/e3d3aa97e37dd21386af3560a76b766120d18211/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/e3d3aa97e37dd21386af3560a76b766120d18211}{MMV-Lab/im2im-paper@e3d3aa9}
on October 27, 2023.

@@

In this paper, we introduce \emph{MMV\_Im2Im} an open-source microscopy machine vision (MMV) toolbox for image-to-image transformation and demonstrate its applications in over 10 biomedical tasks of various types by performing more than 30 experiments. Currently, \emph{MMV\_Im2Im} supports handling 2D\textasciitilde5D microscopy images for supervised image-to-image translation (e.g., labelfree determination {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, imaging modality transformation {[}\protect\hyperlink{ref-WwenuBHa}{5},\protect\hyperlink{ref-UEBDZ3tI}{8}{]}), supervised image restoration {[}\protect\hyperlink{ref-wcCVn8av}{6}{]}, supervised semantic segmentation {[}\protect\hyperlink{ref-TutLhFSz}{9}{]}, supervised instance segmentation {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]}, unsupervised semantic segmentation {[}\protect\hyperlink{ref-RuFP3CS3}{12}{]}, unsupervised image to image translation and synthetization {[}\protect\hyperlink{ref-6wtIu4QY}{13}{]}. The toolbox will continuously grow with more and more methods, ideally also with contributions from the open-source community.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9}{MMV-Lab/im2im-paper@6580cbd}
on October 27, 2023.

@@

In this paper, we introduce \emph{MMV\_Im2Im} an open-source microscopy machine vision (MMV) toolbox for image-to-image transformation and demonstrate its applications in over 10 biomedical tasks of various types by performing more than 30 experiments. Currently, \emph{MMV\_Im2Im} supports handling 2D\textasciitilde5D microscopy images for supervised image-to-image translation (e.g., labelfree determination {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, imaging modality transformation {[}\protect\hyperlink{ref-WwenuBHa}{5},\protect\hyperlink{ref-UEBDZ3tI}{8}{]}), supervised image restoration {[}\protect\hyperlink{ref-wcCVn8av}{6}{]}, supervised semantic segmentation {[}\protect\hyperlink{ref-TutLhFSz}{9}{]}, supervised instance segmentation {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]}, unsupervised semantic segmentation {[}\protect\hyperlink{ref-RuFP3CS3}{12}{]}, unsupervised image to image translation and synthetization {[}\protect\hyperlink{ref-6wtIu4QY}{13}{]}. The toolbox will continuously grow with more and more methods, such as self-supervised learning based methods, ideally also with contributions from the open-source community.
